---
title: "citation regressions"
author: "Juliana Taube"
date: "`r Sys.Date()`"
output: html_document
---

```{r load packages, echo = FALSE, include = FALSE}
library(tidyverse)
library(gamlss)
library(stargazer)
library(ggpubr)
```

```{r create data}
### data functions
is_self_cite <- function(bib_first, bib_last, og_first, og_last){
  # bib_first and _last are first and last authors of cited paper
  # og_first and _last are first and last authors of citing paper
  if(is.na(bib_first) | is.na(bib_last) | is.na(og_first) | is.na(og_last)){
    return(NA)
  }else{
    if(tolower(og_first) %in% c(tolower(bib_first), tolower(bib_last)) | 
       tolower(og_last) %in% c(tolower(bib_first), tolower(bib_last))){
      return(1)
    }else{
      return(0)
    }
  }
}

who_self_cites <- function(bib_first, bib_last, og_first, og_last){
  # bib_first and _last are first and last authors of cited paper
  # og_first and _last are first and last authors of citing paper
  
  if(is.na(bib_first) | is.na(bib_last) | is.na(og_first) | is.na(og_last)){
    return(NA)
  }else if(tolower(og_first) %in% c(tolower(bib_first), tolower(bib_last))){
       return(1) # FA self cites
  }else if(tolower(og_last) %in% c(tolower(bib_first), tolower(bib_last))){
      return(2) # LA self cites
  }else{
      return(0)
    }
}


#### read in data ####
article_data <- read_csv("highlycited/df9_articledata_0.7.csv") %>% 
  mutate(global_north = ifelse(Country == "united kingdom (great britain)", 1, global_north))
  #mutate(Country = ifelse(Country %in% c("england", "scotland", "wales"), "uk", Country))

authorship <- read_csv("highlycited/df9_consensus_authorship.csv") %>% 
  dplyr::select(UT) %>% 
  left_join(article_data, by = "UT") %>%
  ungroup() 

citation <- read_csv("highlycited/df9_consensus_citation.csv") %>% 
  dplyr::select(-PY) %>% 
  # filter to only include citations of valid citing articles
  inner_join(article_data %>% rename(in_bib_of_UT = UT) %>% dplyr::select(in_bib_of_UT),
             by = "in_bib_of_UT") %>%
  # join with cited article data
  inner_join(article_data, by = "UT") %>% 
  # link citation articles to their source bibliography information
  left_join(article_data %>% 
              rename(in_bib_of_AG = AG,
                     in_bib_of_ARbin_ethni = ARbin_ethni,
                     in_bib_of_UT = UT,
                     in_bib_of_first_auth = first_auth,
                     in_bib_of_last_auth = last_auth,
                     in_bib_of_country = Country,
                     in_bib_of_global_north = global_north,
                     in_bib_of_PY = PY) %>%
              dplyr::select(in_bib_of_UT, 
                            in_bib_of_AG, 
                            in_bib_of_ARbin_ethni,
                            in_bib_of_first_auth, 
                            in_bib_of_last_auth,
                            in_bib_of_country,
                            in_bib_of_global_north,
                            in_bib_of_PY)) %>% 
  rowwise() %>% 
  mutate(is_self_cite = is_self_cite(first_auth, 
                                     last_auth, 
                                     in_bib_of_first_auth, 
                                     in_bib_of_last_auth),
         who_self_cite = who_self_cites(first_auth, 
                                         last_auth, 
                                         in_bib_of_first_auth, 
                                         in_bib_of_last_auth)) 


#### make citation counts dfs ####

# times_cited_gn_nosf if filter is_self_cite == 0
# times_cited_gn_nosf_noauth if only include_90, no exceptions for authors
# times_cited_gn if no filter is_self_cite == 0
# times_cited_nosf if filter is_self_cite == 0 but no gn filter

# world but no self cite
times_cited_nosf <- citation %>% 
  left_join(authorship %>% dplyr::select(UT) %>% mutate(author = 1)) %>% 
  filter(include_90 | author == 1) %>%  # relevant citations
  filter(is_self_cite == 0) %>% # remove self citations
  group_by(UT, PY, TC_byfield, author) %>% 
  summarise(num_citations = n()) %>% # these values won't match TC_byfield bc excluding self cite
  ungroup() %>% 
  mutate(citation_rate = num_citations/(2024 - PY)) 

# no self cite but global north
times_cited_gn_nosf <- citation %>% 
  left_join(authorship %>% dplyr::select(UT) %>% mutate(author = 1)) %>% 
  filter(include_90 | author == 1) %>%  # relevant citations
  filter(is_self_cite == 0) %>% # remove self citations
  filter(global_north == 1) %>% #, in_bib_of_global_north == 1) %>% 
  group_by(UT, PY, TC_byfield, author) %>% 
  summarise(num_citations = n()) %>% # these values won't match TC_byfield bc excluding self cite
  ungroup() %>% 
  mutate(citation_rate = num_citations/(2024 - PY)) 

# no self cite but no auth exception  
times_cited_nosf_noauth <- citation %>% 
  left_join(authorship %>% dplyr::select(UT) %>% mutate(author = 1)) %>% 
  filter(include_90) %>%  # relevant citations
  filter(is_self_cite == 0) %>% # remove self citations
  group_by(UT, PY, TC_byfield, author) %>% 
  summarise(num_citations = n()) %>% # these values won't match TC_byfield bc excluding self cite
  ungroup() %>% 
  mutate(citation_rate = num_citations/(2024 - PY)) 

# world but with self cite
times_cited_yessf <- citation %>% 
  left_join(authorship %>% dplyr::select(UT) %>% mutate(author = 1)) %>% 
  filter(include_90 | author == 1) %>%  # relevant citations
  group_by(UT, PY, TC_byfield, author) %>% 
  summarise(num_citations = n()) %>% # these values won't match TC_byfield bc excluding self cite
  ungroup() %>% 
  mutate(citation_rate = num_citations/(2024 - PY)) 



# library(readxl)
# exporter_data <- data.frame()
# for(i in 1:22){
#   print(i)
#   newd <- read_xlsx(path = path, sheet = "ResearchOutput",
#                         col_types = c("text")) # reading all in as text cause easier to convert to # later
#   # newd <- read_excel(paste0("../Alexes' Section/Exporter/Default/highlycited/excel/export part", i, ".xlsx"),
#   #                    sheet = "ResearchOutput",
#   #                    col_types = c("text", "skip", "skip", "skip", "skip", "skip", "skip", "skip", "numeric", "numeric",
#   #                                  "skip", "skip", "skip", "skip", "skip", "skip", "text", "text", "skip", "skip", "skip",
#   #                                  "text", "text", "text", "text", "text", "text", "text", "text", "skip", "skip", "numeric",
#   #                                  "skip", "skip", "skip", "skip", "text", "text", "skip", "skip", "skip", "skip", "skip", "skip",
#   #                                  "text", "text", "text", "text", "text", "text", "skip", "skip", "skip", "skip", "skip")) %>%
#   #   rename(UT = `Accession Number (UT)`)
#   exporter_data <- exporter_data %>% bind_rows(newd)
# }
# write_csv(title_data, "highlycited/exporter_data.csv")

exporter_data <- read_csv("highlycited/exporter_data.csv",
                         col_types = "cccccccccccccccccccccccccccccccccccccccccccccccccccc") %>% 
  select(`Accession Number (UT)`, `Number of Cited References`, `Times Cited`, `Keywords`, 
           `Keywords Plus`, 
           `1st Subject Category (traditional)`, `2nd Subject Category (traditional)`,  
           `Abstract`, `Published Year`, `ISSN`, `EISSN`, `Source title`, 
           `Title`) %>% 
  rename(UT = `Accession Number (UT)`)


# needs to have dash for WoS/JCR
#### get exporter ISSNs to match to WoS ####
exporter_issns_for_jcr <- exporter_data %>% 
  # filter to our articles in 90th percentile + authorship
  left_join(citation %>% dplyr::select(UT, include_90)) %>% 
  left_join(authorship %>% dplyr::select(UT) %>% mutate(author = 1)) %>% 
  filter(include_90 | author == 1) %>%  # relevant citations
  # filter to unique journals
  dplyr::select(ISSN, EISSN, `Source title`) %>% 
  distinct() %>% 
  #distinct(ISSN, EISSN, .keep_all = T) %>% 
  #mutate(issn_for_wos = ifelse(is.na(ISSN), EISSN, ISSN))
  # include both issn and eissn in case they don't have both
  pivot_longer(cols = c(ISSN, EISSN), names_to = "issn_type", values_to = "issn") %>% 
  filter(! is.na(issn)) %>% 
  select(-issn_type) %>% 
  distinct(issn) 

already_downloaded <- read_xlsx("highlycited/issns/batch0_240719.xlsx",
                                skip = 2) %>% 
  select(ISSN, eISSN) %>% 
  pivot_longer(cols = c(ISSN, eISSN), names_to = "issn_type", values_to = "issn") %>% 
  filter(issn != "N/A") %>% 
  distinct(issn)

issns_todo <- exporter_issns_for_jcr %>% 
  # want issns in exporter that aren't already downloaded
  anti_join(already_downloaded) %>% 
  mutate(batch_num = ceiling(row_number()/600))

write_csv(issns_todo, "highlycited/issns/exporter_issns_20240719.csv")

#### read in JCRs!!! ####
# I manually deleted last two rows that have text & not data
library(readxl)
batchs <- seq(0, 5, by = 1)
jcr_df <- data.frame()
for(b in batchs){
  batch_data <- read_xlsx(paste0("highlycited/issns/batch", b, "_240719.xlsx"),
                          skip = 2) %>% 
    dplyr::select(ISSN, eISSN, `Journal name`, `2023 JIF`) %>% 
    rename(JIF = `2023 JIF`) %>% 
    distinct() %>% 
    mutate(ISSN = ifelse(ISSN == "N/A", NA, ISSN),
           eISSN = ifelse(eISSN == "N/A", NA, eISSN),
           JIF = ifelse(JIF == "N/A", NA, 
                        ifelse(JIF == "<0.1", 0.01,
                               JIF)),
           JIF = as.integer(JIF))
  
  jcr_df <- jcr_df %>% bind_rows(batch_data)
                          
}

#### join JCR with exporter data ####

attempt_join <- exporter_data %>%
  dplyr::select(ISSN, EISSN, UT, `Source title`) %>% 
  pivot_longer(cols = c(ISSN, EISSN), names_to = "issn_type", values_to = "issn") %>% 
  dplyr::select(-issn_type) %>% 
  filter(! is.na(issn)) %>% 
  distinct() %>% 
  left_join(jcr_df %>% 
              pivot_longer(cols = c(ISSN, eISSN), 
                           names_to = "issn_type", values_to = "issn") %>% 
              dplyr::select(-issn_type) %>% 
              filter(!is.na(issn)) %>% 
              distinct()) %>% 
  dplyr::select(UT, JIF) %>% 
  filter(! is.na(JIF)) %>% 
  distinct()


#### create regression data ####

# note several different options for times_cited df in first line, run with each
  # times_cited_nosf
  # times_cited_gn_nosf
  # times_cited_nosf_noauth
  # times_cited_yessf

regression_df <- times_cited_yessf %>% 
  left_join(article_data, by = c("UT", "PY")) %>% 
  left_join(attempt_join) %>% 
  left_join(exporter_data) %>% 
  filter(! is.na(JIF)) %>% 
  filter(! grepl("U", AG)) %>%  # 36k papers, 24% under new constraints
  filter(! grepl("U", ARbin_ethni)) %>% # 55k papers, 65% under new constraints
  #filter(global_north == 1) %>% 
  rename(num_cited_refs = `Number of Cited References`) %>% 
  #filter(JIF > 0) %>% 
  mutate(AG = as.factor(AG),
         ARbin_ethni = as.factor(ARbin_ethni),
         log_num_citations = log(num_citations),
         log_citation_rate = log(citation_rate)) %>%
  dplyr::select(UT, AG, ARbin_ethni, FA_genderize, LA_genderize,
                FA_binrace_ethni, LA_binrace_ethni,
                JIF, PY, num_citations,
                log_num_citations, citation_rate, log_citation_rate,
                WC, num_cited_refs, `1st Subject Category (traditional)`, Country,
                global_north) %>%
  filter(! is.na(global_north))
  # mutate(across(c(num_citations, citation_rate, JIF, num_cited_refs, PY),
  #               ~scale(.x)[,1], # scale adds [,1]to name
  #               .names = "z_{.col}")) 
out <- regression_df %>% 
  rename(pair_gender = AG,
         pair_race = ARbin_ethni,
         FA_gender = FA_genderize,
         LA_gender = LA_genderize,
         FA_race = FA_binrace_ethni,
         LA_race = LA_binrace_ethni,
         year = PY,
         WC_1st = `1st Subject Category (traditional)`)
write_csv(out, "highlycited/input_jif_regression_yessf_20240925.csv")

```

The only change from the above code is that `article_id` is substituted for `UT`.

```{r hide uts}
key_map <- read_csv("highlycited/key_ut_to_articleid.csv")

df <- read_csv("highlycited/input_jif_regression_nosf_20240925.csv") %>% 
  left_join(key_map) %>% select(-UT)
df_gn <- read_csv("highlycited/input_jif_regression_gn_nosf_20240925.csv") %>%
  left_join(key_map) %>% select(-UT)
df_sf <- read_csv("highlycited/input_jif_regression_yessf_20240925.csv") %>% 
  left_join(key_map) %>% select(-UT)
df_noauth <- read_csv("highlycited/input_jif_regression_nosf_noauth_20240925.csv") %>% 
  left_join(key_map) %>% select(-UT)
  
write_csv(df, "highlycited/input_jif_regression_nosf_20240925_public.csv")
write_csv(df_gn, "highlycited/input_jif_regression_gn_nosf_20240925_public.csv")
write_csv(df_sf, "highlycited/input_jif_regression_yessf_20240925_public.csv")
write_csv(df_noauth, "highlycited/input_jif_regression_nosf_noauth_20240925_public.csv")
```

## To run this using public data, start here

```{r load data}
df <- read.csv("highlycited/input_jif_regression_nosf_20240925_public.csv",header=TRUE) %>%
  mutate(log10_citation_rate = log10(citation_rate),
         binJIF = as.integer(JIF>10),
         sqrtJIF = sqrt(JIF),
         pair_race_bin = ifelse(pair_race == "WW", "WW", "PorP")) %>% 
  mutate(pair_gender = as.factor(pair_gender),
         pair_race = as.factor(pair_race),
         pair_race_bin = as.factor(pair_race_bin))

df$pair_race <- factor(df$pair_race, levels = c("WW", "WN", "NW", "NN"))
df$pair_race_bin <- factor(df$pair_race_bin, levels = c("WW", "PorP"))
df$global_north <- factor(df$global_north, levels = c("0", "1"))
```

### Explore and check data

Note that to create this data I removed all entries where both first and last author gender and race could not be inferred. If we want more power, could do separate analyses with complete cases of each identity type.

Examine distribution of citation rates and journal impact factors

```{r histograms}
hist(df$log10_citation_rate)

hist(df$JIF)
hist(df$sqrtJIF)
```

Check whether first and last author gender and first and last author race are independent. This affects whether we use pair_gender and pair_race variables or independent first and last author variables.

```{r gender xi squared test}
table(df$FA_gender,df$LA_gender) # cols are LA, rows are FA
# chisquared test is to determine whether two categorical variables are independent
Xsq <- chisq.test(table(df$FA_gender,df$LA_gender))
Xsq
Xsq$expected
```
Does this conflict with our finding that there aren't gender collaboration biases? 


```{r race xi squared test}
table(df$FA_race,df$LA_race) # cols are LA, rows are FA
# chisquared test is to determine whether two categorical variables are independent
Xsq <- chisq.test(table(df$FA_race,df$LA_race))
Xsq
Xsq$expected
```

Basically we observe more gender and race assortativity/homophily than expected.

Look at collinearity between JIF and gender and JIF and race

```{r collinearity}
df %>% ggplot(aes(x = pair_gender, y = sqrtJIF)) + 
  geom_jitter(alpha = 0.15, col = "dimgrey") + 
  geom_boxplot(fill = NA, outlier.shape = NA) + 
  theme_bw()
df %>% ggplot(aes(x = pair_race, y = sqrtJIF)) + 
  geom_jitter(alpha = 0.15, col = "dimgrey") + 
  geom_boxplot(fill = NA, outlier.shape = NA) + 
  theme_bw()
df %>% ggplot(aes(x = pair_race_bin, y = sqrtJIF)) + 
  geom_jitter(alpha = 0.15, col = "dimgrey") + 
  geom_boxplot(fill = NA, outlier.shape = NA) + 
  theme_bw()

# Table S2
anova_lm_gender <- lm(sqrtJIF ~ pair_gender, data = df)
summary(anova_lm_gender)
stargazer(anova_lm_gender, style = "all", covariate.labels = c("MW", "WM", "WW"))

anova_gender <- aov(sqrtJIF ~ pair_gender, data = df)
summary(anova_gender)

# Table S3
anova_lm_race <- lm(sqrtJIF ~ pair_race, data = df)
summary(anova_lm_race)
stargazer(anova_lm_race, style = "all", covariate.labels = c("EC", "CE", "CC"))

anova_race <- aov(sqrtJIF ~ pair_race, data = df)
summary(anova_race)

anova_lm_race_bin <- lm(sqrtJIF ~ pair_race_bin, data = df)
summary(anova_lm_race_bin)
anova_race_bin <- aov(sqrtJIF ~ pair_race_bin, data = df)
summary(anova_race_bin)

anova_lm_tog <- lm(sqrtJIF ~ pair_gender + pair_race, data = df)
summary(anova_lm_tog)

anova_tog <- aov(sqrtJIF ~ pair_gender + pair_race_bin, data = df)
summary(anova_tog)

# multiple comparisons another way to know which groups are different..but I'm not sure this is our aim
```

race doesn't seem to be collinear with JIF, but gender does for GN 
both are collinear, though gender less so for world

```{r anova assumptions}
# do I need to check any ANOVA assumptions?

# 1. normal distribution of data within group
df %>% ggplot(aes(x = sqrtJIF)) + 
  geom_histogram() +
  facet_wrap(~pair_gender) +
  theme_bw()
df %>% ggplot(aes(x = sqrtJIF)) + 
  geom_histogram() +
  facet_wrap(~pair_gender) +
  theme_bw()
# not met, but not too sensitive
# can use kruskal wallis instead

# 2. standard deviations are equal within groups
df %>% group_by(pair_gender) %>% 
  summarise(sd = sd(sqrtJIF))
df %>% group_by(pair_race) %>% 
  summarise(sd = sd(sqrtJIF))
# looks good
```


## Run regression models

```{r models}
# Table S4
fit_gender_nojif <- lm(log10_citation_rate ~ pair_gender, data = df)
summary(fit_gender_nojif)
stargazer(fit_gender_nojif, style = "all", covariate.labels = c("MW", "WM", "WW"))

# Table S5
fit_race_nojif <- lm(log10_citation_rate ~ pair_race, data = df)
summary(fit_race_nojif)
stargazer(fit_race_nojif, style = "all", covariate.labels = c("EC", "CE", "CC"))

# Table S6
fit_gender <- lm(log10_citation_rate ~ pair_gender*sqrtJIF, data = df)
summary(fit_gender)
stargazer(fit_gender, style = "all", covariate.labels = c("MW", "WM", "WW", "JIF",
                                                          "MW:JIF", "WM:JIF", "WW:JIF"))
# Table S7
fit_race <- lm(log10_citation_rate ~ pair_race*sqrtJIF, data = df)
summary(fit_race)
stargazer(fit_race, style = "all", covariate.labels = c("EC", "CE", "CC", "JIF",
                                                          "EC:JIF", "CE:JIF", "CC:JIF"))
# Table S8
fit_nogn <- lm(log10_citation_rate ~ pair_gender*sqrtJIF + pair_race*sqrtJIF, data = df)
summary(fit_nogn)
stargazer(fit_nogn, style="all", covariate.labels = c("MW", "WM", "WW", "JIF",
                                                      "EC", "CE", "CC",
                                                 "MW:JIF", "WM:JIF", "WW:JIF", "EC:JIF",
                                                 "CE:JIF", "CC:JIF"))

# main text
fit <- lm(log10_citation_rate ~ pair_gender*sqrtJIF + pair_race*sqrtJIF + global_north, data = df)
summary(fit)
stargazer(fit, style="all", covariate.labels = c("MW", "WM", "WW", "JIF", "EC", "CE", "CC",
                                                 "Global North Senior Author",
                                                 "MW:JIF", "WM:JIF", "WW:JIF", "EC:JIF",
                                                 "CE:JIF", "CC:JIF"))



# fit_gender_race_nojif <- lm(log10_citation_rate ~ pair_gender + pair_race, data = df)
# summary(fit_gender_race_nojif)

```


```{r sensitivity geography}
df_gn <- read_csv("highlycited/input_jif_regression_gn_nosf_20240925_public.csv") %>%
  dplyr::select(article_id, year, num_citations, citation_rate, pair_gender, pair_race, FA_gender, LA_gender, FA_race, LA_race, JIF, WC_1st, num_cited_refs, Country) %>% 
  rename(WC = WC_1st, country = Country) %>% 
  mutate(log10_citation_rate = log10(citation_rate),
         sqrtJIF = sqrt(JIF),
         pair_race_bin = ifelse(pair_race == "WW", "WW", "PorP")) %>% 
  mutate(pair_gender = as.factor(pair_gender),
         pair_race = as.factor(pair_race),
         pair_race_bin = as.factor(pair_race_bin))

df_gn$pair_race <- factor(df_gn$pair_race, levels = c("WW", "WN", "NW", "NN"))
df_gn$pair_race_bin <- factor(df_gn$pair_race_bin, levels = c("WW", "PorP"))

# only gender interactions significant/collinear
anova_lm_gender <- lm(sqrtJIF ~ pair_gender, data = df_gn)
summary(anova_lm_gender)

anova_lm_race <- lm(sqrtJIF ~ pair_race, data = df_gn)
summary(anova_lm_race)

fit_gender <- lm(log10_citation_rate ~ pair_gender*sqrtJIF, data = df_gn)
summary(fit_gender)

# race not predictive when focused on just global north
fit_race <- lm(log10_citation_rate ~ pair_race*sqrtJIF, data = df_gn)
summary(fit_race)

# Table S10
fit <- lm(log10_citation_rate ~ pair_gender*sqrtJIF + pair_race*sqrtJIF, data = df_gn)
summary(fit)
stargazer(fit, style = "all", covariate.labels = c("MW", "WM", "WW", "JIF", 
                                                   "WN", "NW", "NN", "MW:JIF",
                                                   "WM:JIF", "WW:JIF", "EC:JIF",
                                                   "CE:JIF", "CC:JIF"))
# race becomes significant for gn population
# fit_gender_nojif <- lm(log10_citation_rate ~ pair_gender, data = df_gn)
# summary(fit_gender_nojif)
# 
# fit_race_nojif <- lm(log10_citation_rate ~ pair_race, data = df_gn)
# summary(fit_race_nojif)
# 
# fit_gender_race_nojif <- lm(log10_citation_rate ~ pair_gender + pair_race, data = df_gn)
# summary(fit_gender_race_nojif)


```

```{r sensitivity self cite}
# include self citations
df_sf <- read_csv("highlycited/input_jif_regression_yessf_20240925_public.csv") %>% 
  dplyr::select(article_id, year, num_citations, citation_rate, pair_gender, pair_race, FA_gender,
                LA_gender, FA_race, LA_race, JIF, WC_1st, num_cited_refs, Country, global_north) %>% 
  rename(WC = WC_1st, country = Country) %>% 
  mutate(log10_citation_rate = log10(citation_rate),
         sqrtJIF = sqrt(JIF),
         pair_race_bin = ifelse(pair_race == "WW", "WW", "PorP")) %>% 
  mutate(pair_gender = as.factor(pair_gender),
         pair_race = as.factor(pair_race),
         pair_race_bin = as.factor(pair_race_bin))

df_sf$pair_race <- factor(df_sf$pair_race, levels = c("WW", "WN", "NW", "NN"))
df_sf$pair_race_bin <- factor(df_sf$pair_race_bin, levels = c("WW", "PorP"))
df_sf$global_north <- factor(df_sf$global_north, levels = c("0", "1"))

anova_lm_gender <- lm(sqrtJIF ~ pair_gender, data = df_sf)
summary(anova_lm_gender)

anova_lm_race <- lm(sqrtJIF ~ pair_race, data = df_sf)
summary(anova_lm_race)
stargazer(anova_lm_race, style = "all")
# now race is collinear

# chisquared test is to determine whether two categorical variables are independent
Xsq <- chisq.test(table(df_sf$FA_gender,df_sf$LA_gender))
Xsq
Xsq <- chisq.test(table(df_sf$FA_race,df_sf$LA_race))
Xsq


fit_gender <- lm(log10_citation_rate ~ pair_gender*sqrtJIF, data = df_sf)
summary(fit_gender)

# table S9
fit <- lm(log10_citation_rate ~ pair_gender*sqrtJIF + pair_race*sqrtJIF + global_north, data = df_sf)
summary(fit)
stargazer(fit, style = "all", covariate.labels = c("MW", "WM", "WW", "JIF", "EC", "CE", "CC",
                                                   "Global North Senior Author", "MW:JIF",
                                                   "WM:JIF", "WW:JIF", "EC:JIF", "CE:JIF",
                                                   "CC:JIF"))

```



```{r sensitivity authorship}
df_noauth <- read_csv("highlycited/input_jif_regression_nosf_noauth_20240925_public.csv") %>% 
  dplyr::select(article_id, year, num_citations, citation_rate, pair_gender, pair_race, FA_gender,
                LA_gender, FA_race, LA_race, JIF, WC_1st, num_cited_refs, Country, global_north) %>% 
  rename(WC = WC_1st, country = Country) %>% 
  mutate(log10_citation_rate = log10(citation_rate),
         sqrtJIF = sqrt(JIF),
         pair_race_bin = ifelse(pair_race == "WW", "WW", "PorP")) %>% 
  mutate(pair_gender = as.factor(pair_gender),
         pair_race = as.factor(pair_race),
         pair_race_bin = as.factor(pair_race_bin))

df_noauth$pair_race <- factor(df_noauth$pair_race, levels = c("WW", "WN", "NW", "NN"))
df_noauth$pair_race_bin <- factor(df_noauth$pair_race_bin, levels = c("WW", "PorP"))
df_noauth$global_north <- factor(df_noauth$global_north, levels = c("0", "1"))

anova_lm_gender <- lm(sqrtJIF ~ pair_gender, data = df_noauth)
summary(anova_lm_gender)

anova_lm_race <- lm(sqrtJIF ~ pair_race, data = df_noauth)
summary(anova_lm_race)
stargazer(anova_lm_race, style = "all")
# now race is collinear but gender isn't!

# chisquared test is to determine whether two categorical variables are independent
Xsq <- chisq.test(table(df_noauth$FA_gender,df_noauth$LA_gender))
Xsq
Xsq <- chisq.test(table(df_noauth$FA_race,df_noauth$LA_race))
Xsq

# table s11
fit <- lm(log10_citation_rate ~ pair_gender*sqrtJIF + pair_race*sqrtJIF + global_north, data = df_noauth)
summary(fit)
stargazer(fit, style = "all", covariate.labels = c("MW", "WM", "WW", "JIF", "EC", "CE", "CC",
                                                   "Global North Senior Author", "MW:JIF",
                                                   "WM:JIF", "WW:JIF", "EC:JIF", "CE:JIF",
                                                   "CC:JIF"))

```